## Course Project

### Summary 
    In this project , we are asked to make a report , tidy dataset, and codebook presented in github
    The datassource is collected from the accelerometers from the Samsung Galaxy S smartphone.
    We can obtain data from the UCI Machine Learning Repository website(*1)
    To output the required tidy datset , we must do some data cleanning and transformation on data and
    record them in a markdown file.

    * 1 data soruce :http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones 
    
### Step 1 Merge train and test data and measuremen values

```{r cache=TRUE}
###
### loadData(type)
## - load data and merge ydata and measuerment values 
##   for test or train
## - 'type': indicating test or train data
###

loadData<- function (type){
  #load data 
  folder<-"UCI HAR Dataset/"
  filetype<-".txt"

  subjects<-read.table(paste(folder, type,"/subject_",type,filetype, sep=""))
  y <- read.table(paste(folder, type,"/y_",type,filetype, sep=""))
  
  featuresName<- read.table(paste(folder, "features",filetype, sep=""))
  x <- read.table(paste(folder, type,"/X_",type,filetype, sep=""))

  # Put header of the feature value with features name
  names(x)<-featuresName[,2]
  

  # Put header of the activity value and subject with proper name 
  colnames(subjects) <- 'subject'
  colnames(y) <- 'activity'          
            
            
  # Combine the y ,subject and x together 
  df<- cbind(cbind(subjects,y), x)
  return(df)
}
setwd("/Develop/R/Coursera/Course3/")
test<-loadData("test")
train<-loadData("train")

fulData<-rbind(train,test)
```

### Step 2 replace activity with descriptive activity name 
```{r cache=TRUE}
# Replace the activity with corrsponding activity name
activityNames<- read.table("UCI HAR Dataset/activity_labels.txt")
fulData$activity<-sapply(fulData$activity,function(x) activityNames[x,2])
```

### Step 3 Keep measurements respresented for mean and standard deciation 
```{r cache=TRUE}
# Keep features that represents for mean and standard deviation (std)

featuresNames<- read.table("UCI HAR Dataset/features.txt")
colnames(featuresNames)<-c("fId","featurename")
keepFeatures =subset(featuresNames,grepl("mean|std",featurename))[,2]

# Select the features we want
preData<- subset(fulData,select =c(cbind('subject','activity'),as.character(keepFeatures)))

```

### Step 4 Create a dataframe with identity vaiable "subject" and "activity" 
```{r cache=TRUE}

# Use reshape library to create a dataframe with identity vaiable "subject" and "activity" 
library(reshape)
tidyMelted<-melt(preData,id=c("subject","activity"))

```
### Step 5 Create the tidy data with measurements with respect to each subject and activities
        - This Rows: 180 (30 sujbect x 6 activities) with 81 columns
```{r cache=TRUE}
tidy <- cast(tidyMelted, subject+activity~variable, mean)
dim(tidy) # See the row and column number
summary(tidy)
```

### Step 6 Output tidy as tidy.txt and tidy.csv
```{r }
write.table(tidy,"tidy.txt")
write.csv(tidy,"tidy.csv")
```
